---
title: "Untitled"
author: "Abhinav Sehgal"
date: "24/10/2020"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Introduction
Took the data generated by the following study (http://groupware.les.inf.puc-rio.br/har.
I'll include the following things: question, data input, features, algorithm, parameters and evaluation.

### Question Statement

According to the study afore mentioned: "Six young health participants were asked to perform one set of 10 repetitions of the Unilateral Dumbbell Biceps Curl in five different fashions: exactly according to the specification (Class A), throwing the elbows to the front (Class B), lifting the dumbbell only halfway (Class C), lowering the dumbbell only halfway (Class D) and throwing the hips to the front (Class E).
Class A Corresponds to the specified execution of the exercise, while the other 4 classes Correspond to common mistakes."
Our goal is to predict the manner in which they did the exercise.

### cleaning Data 



```{r}
library(data.table)
library(rpart)


library(caret)

```

```{r}
TrainD <- read.csv("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv", header=T, na.strings=c("NA","#DIV/0!",""))
TestD <- read.csv("http://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv", header=T, na.strings=c("NA","#DIV/0!",""))
dim(TrainD)
dim(TestD)
```

TensorFlow is an end-to-end open source platform for machine learning. It has a comprehensive, flexible ecosystem of tools, libraries and community resources that lets researchers push the state-of-the-art in ML and developers easily build and deploy ML powered applications.

```{r}
names(TrainD)
```

Build and train ML models easily using intuitive high-level APIs like Keras with eager execution, which makes for immediate model iteration and easy debugging.
```{r}
LNA<- sapply(TrainD, function (x) any(is.na(x)))
NTD <- subset(TrainD, select=c("classe", names(LNA)[!LNA & grepl("belt|[^(fore)]arm|dumbbell|forearm", names(LNA))]))
```

convert classe to a Factor data type, so that caret builds a classification rather than of a regression model.

Train d - 60 
test d = 40
```{r}
inTrain <- createDataPartition(NTD$classe, p=0.6, list=FALSE)
Train_data <-  NTD[inTrain, ]
Test_data <- NTD[-inTrain, ]
```
Easily train and deploy models in the cloud, on-prem, in the browser, or on-device no matter what language you use.
```{r}
NZV <- nearZeroVar(Train_data, saveMetrics=TRUE)
NZV
```




I use a plot to display the result in a best manner.

```{r}

```

The plot show the relationship between the number of PLS components and the resampled estimate of the area under the ROC curve.
And then, finally, I take a look to the confusion matrix and associated statistics.


I can apply another model like the "regularized discriminant analysis" model 


The accuracy of this model is 99.5%
I look closely to the final model, i can extract the variables that compone the model and see the confusion matrix of this model with the class.error. The class error is less tha 1%
TensorFlow
Install
Learn
Introduction
New to TensorFlow?
TensorFlow
The core open source ML library
For JavaScript
TensorFlow.js for ML using JavaScript
For Mobile & IoT
TensorFlow Lite for mobile and embedded devices
For Production
TensorFlow Extended for end-to-end ML components
Swift for TensorFlow (in beta)
API
TensorFlow (r2.3)
r1.15
Versions…
TensorFlow.js
TensorFlow Lite
TFX
Resources
Responsible AI
Resources and tools to integrate Responsible AI practices into your ML workflow
Models & datasets
Pre-trained models and datasets built by Google and the community
Tools
Ecosystem of tools to help you use TensorFlow
Libraries & extensions
Libraries and extensions built on TensorFlow
TensorFlow Certificate program
Differentiate yourself by demonstrating your ML proficiency
Learn ML
Educational resources to learn the fundamentals of ML with TensorFlow
Community
Why TensorFlow
About
Case studies
Trusted Partner Program
Search
Language
GitHub
Sign in
Google is committed to advancing racial equity for Black communities. See how.

Why TensorFlow
TensorFlow is an end-to-end open source platform for machine learning. It has a comprehensive, flexible ecosystem of tools, libraries and community resources that lets researchers push the state-of-the-art in ML and developers easily build and deploy ML powered applications.

About  

Easy model building
Build and train ML models easily using intuitive high-level APIs like Keras with eager execution, which makes for immediate model iteration and easy debugging.


Robust ML production anywhere
Easily train and deploy models in the cloud, on-prem, in the browser, or on-device no matter what language you use.


Powerful experimentation for research
A simple and flexible architecture to take new ideas from concept to code, to state-of-the-art models, and to publication faster.

Solutions to common ML problems
Simple step-by-step walkthroughs to solve common ML problems with TensorFlow.


For beginners
Your first neural network
Train a neural network to classify images of clothing, like sneakers and shirts, in this fast-paced overview of a complete TensorFlow program.


For experts
Generative adversarial networks
Train a generative adversarial network to generate images of handwritten digits, using the Keras Subclassing API.


For experts
Neural machine translation with attention
Train a sequence-to-sequence model for Spanish to English translation using the Keras Subclassing API.

Powered by TensorFlow
A diverse community of developers, enterprises and researchers are using ML to solve challenging, real-world problems. Learn how their research and applications are being #PoweredbyTF and how you can share your story.



Developers
Helping doctors detect respiratory diseases using machine learning
Watch the video  


Enterprise
Categorizing Airbnb listing photos using TensorFlow
Watch the video  


Research
Enabling medical staff to prescribe the right antibiotics with TensorFlow
Watch the video  
Companies using TensorFlow
See case studies  
News & announcements
Check out the TensorFlow blog for additional updates, and subscribe to our monthly TensorFlow newsletter to get the latest announcements sent directly to your inbox.

Sign up  

June 29, 2020
Integrate Responsible AI practices into your ML workflow
TensorFlow is committed to helping make progress in the responsible development of AI by sharing a collection of resources and tools with the ML community.

Learn more  

Mar 16, 2020
Google Developers Machine Learning Crash Course
The Machine Learning Crash Course is a self-study guide for aspiring machine learning practitioners featuring a series of lessons with video lectures, real-world case studies, and hands-on practice exercises.

Learn more  

Mar 12, 2020
TensorFlow Dev Summit 2020 Recap
Our virtual Dev Summit brought announcements of TensorFlow 2.2 plus many new features and additions to the ecosystem! Read the recap on our blog to learn about the updates and watch video recordings of every session.

Learn more  

Mar 10, 2020
Differentiate yourself with the TensorFlow Developer Certificate
Check out our TensorFlow Certificate program for practitioners to showcase their expertise in machine learning in an increasingly AI-driven global job market.

Learn more  
Resources and community support
We are committed to fostering an open and welcoming ML community. Join the TensorFlow community and help grow the ecosystem.

Community  
Responsible AI DevPost Challenge 
Use TensorFlow 2.2 to build a model or application with AI Principles in mind. As you build, ask questions related to fairness, privacy, and security.

